Environment reconstruction is an active field of research, particularly from the Simultaneous Localization and Mapping (SLAM) community\cite{Thrun2008_SLAM}. \textbf{SMALL DESCRIPTION OF SLAM!!!} GPS unreliable because it's not precise, a couple of meters of difference could lead a car jumping on the curve or bumping another while trying to park.

Most research has cameras and a mixture of exotic depth sensors as inputs. One implication of this type of input is large quantities of information having to be processed, thus, needing high-performance and power-hungry devices to execute their algorithms. This is something that limits the actual utility of such systems for mobile applications.

Another disadvantage to using ``classic'' approaches is that computational resources would need to be shared inefficiently (i.e. a processor would have to switch between a facial recognition algorithm to a depth-estimation one). Having a neuro inspired system means that the tasks are executed by the same network/algorithm.

Humans are able to do something similar with an efficient highly-parallel neural computing system that requires about 20-watts to function. How exactly this is done in the brain is still an open question. This research will provide a solution, inspired by state-of-the-art neuroscience, to the environment reconstruction problem using neuromorphic hardware.

SpiNNaker provides a massively-parallel high-efficiency computing platform, inspired by the brain. It's an excellent choice for neuroscience research, particularly to study spiking neural networks. Its software stack has many ready-to-use neuron models and development can be performed in a straight forward manner. 

