\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2.5cm,right=2.5cm,top=2cm,bottom=2cm]{geometry}
\title{Article responses}
\begin{document}
\maketitle
\begin{itemize}
	\item[Reply to:]Julio Vega Hern\'andez.\\
	I agree with the lack of proper structure for an end-of-first-year short report. Since it's going to take longer than the time we've got to fix this, I'll just put the section names, modify accordingly  and do as much as I can on what might be missing.\\
	I've added a short review of image/video encoding techniques.\\
    I don't think there is any need for code/implementation details.
\item[Reply to:] Malte Vespar.\\
	I'm still defining where to go from the current state of my work. The contribution so far is to generate a real-time, biologically plausible, neural encoder that only requires off-the-shelf components. This, to the best of my knowledge, has not been achieved.
	The loop unrolling may be done by the compiler, though in my tests, it was not
	giving the expected results.
	I've added images to explain tiled convolution advantages.
	Images in figure 4 where stand-ins for actual results, these has been corrected.
\item[Reply to:] Raul Garc\'ia.\\
	I've run a spell check now.
\item[Reply to:] Norafiza Binti Sahlan.\\
	Diagrams have been modified.
\item[Reply to:] Syed Shaukat. \\
	I've run a spell check and asked people to proof-read it.
\item[Reply to:] Fernando Ren\'e S\'anchez Serrano. \\
	I've added a table of contents at the beginning of the paper.
\end{itemize}
\end{document}